# Initializing interactive session
```{bash}
srun --ntasks=1 --cpus-per-task=1 --mem=100G --time=240:00:00 --pty bash
module load gcc
module load plink/2.0
module load miniconda3
conda activate r_env
module load bcftools
```

# Identifying individuals to include from GTEx
```{bash}
# copying files over from Meri's directory to identify sample lists for mapping mQTLs
for tissue in BreastMammaryTissue ColonTransverse KidneyCortex Lung MuscleSkeletal Ovary Prostate Testis WholeBlood
do
  echo $tissue
  cp /gpfs/data/gtex-group/mpavia/methylation/data/Phenotypes/bedfiles/${tissue}.bed.gz /gpfs/data/pierce-lab/james.li/imQTL/data/GTEx/eligible_gtex_samples/${tissue}.bed.gz
  cp /gpfs/data/gtex-group/mpavia/methylation/data/Covariates/${tissue}.covariates.txt /gpfs/data/pierce-lab/james.li/imQTL/data/GTEx/eligible_gtex_samples/${tissue}.covariates.txt
done

# outputting eligible sample lists for GTEx samples
for tissue in BreastMammaryTissue ColonTransverse KidneyCortex Lung MuscleSkeletal Ovary Prostate Testis WholeBlood
do
  echo ${tissue}
  Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/IDENTIFY_ELIGIBLE_GTEX_SAMPLES.R ${tissue}
done
```

# Preprocessing all the genetic data
```{bash}
bash /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/PROCESSING_GENETIC_DATA.sh
```

# Generating PCs for GTEX and HEALS genetic data
```{bash}
for o in GTEx HEALS
do
  sbatch --export=ARGS1=${o} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/PLINK2_PCA.sh
done
```

# Identifying samples to include in mQTL analysis by filtering for individuals with methylation, genotyping, and covariate data
```{r}
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/GTEx_INCLUDE_INDIVIDUALS.R
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/HEALS_INCLUDE_INDIVIDUALS.R
```

# Estimating cell type fractions in each tissue
```{r}
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/GTEx_ESTIMATE_CELLTYPE.R
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/HEALS_ESTIMATE_CELLTYPE.R
```

# Converting DNAm data to M-values and then applying a rank-based inverse normal transform (INT)
```{r}
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/GTEx_PROCESSING_DNAM.R
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/HEALS_PROCESSING_DNAM.R
```

# Assembling covariate files
```{r}
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/GTEx_ASSEMBLING_COVARIATE_FILES.R
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/HEALS_ASSEMBLING_COVARIATE_FILES.R
```

# Utilizing tensorQTL to map imQTLs
```{bash}
#SBATCH -p gpuq
#SBATCH --gres gpu:1
# srun --pty -p gpuq --gres gpu:1 /bin/bash

##########################
# MAPPING imQTLS [BEST ONLY]
for dataset in HEALS GTEx
do
  # set working directory
  cd /gpfs/data/pierce-lab/james.li/imQTL/input/${dataset}
  # loop to submit jobs for each tissue and cell type
  for tissue in `ls *.bed | cut -d"." -f1`
  do
    # obtaining list of cell types for current tissue
    tmp_cell_type_list=`ls processed_interactions_${tissue}_*.txt | cut -d"_" -f4 | cut -d"." -f1`
    # submitting tensorQTL jobs for each tissue and cell type
    for cell_type in $tmp_cell_type_list
    do
      echo $dataset $tissue $cell_type
      sbatch --export=ARGS1=${dataset},ARGS2=${tissue},ARGS3=${cell_type} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/tensorQTL_imQTL_BEST_ONLY.sh
    done
  done
done

##########################
# MAPPING imQTLS [ALL]
for dataset in HEALS GTEx
do
  # set working directory
  cd /gpfs/data/pierce-lab/james.li/imQTL/input/${dataset}
  # loop to submit jobs for each tissue and cell type
  for tissue in `ls *.bed | cut -d"." -f1`
  do
    # obtaining list of cell types for current tissue
    tmp_cell_type_list=`ls processed_interactions_${tissue}_*.txt | cut -d"_" -f4 | cut -d"." -f1`
    # submitting tensorQTL jobs for each tissue and cell type
    for cell_type in $tmp_cell_type_list
    do
      echo $dataset $tissue $cell_type
      sbatch --export=ARGS1=${dataset},ARGS2=${tissue},ARGS3=${cell_type} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/tensorQTL_imQTL_ALL.sh
    done
  done
done

##########################
# MAPPING mQTLs [BEST ONLY]
for dataset in HEALS GTEx
do
  # set working directory
  cd /gpfs/data/pierce-lab/james.li/imQTL/input/${dataset}
  # loop to submit jobs for each tissue type
  for tissue in `ls *.bed | cut -d"." -f1`
  do
    # submitting tensorQTL jobs for each tissue type
    echo $dataset $tissue
    sbatch --export=ARGS1=${dataset},ARGS2=${tissue} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/tensorQTL_mQTL_BEST_ONLY.sh
  done
done

##########################
# MAPPING mQTLs [ALL]
for dataset in HEALS GTEx
do
  # set working directory
  cd /gpfs/data/pierce-lab/james.li/imQTL/input/${dataset}
  # loop to submit jobs for each tissue type
  for tissue in `ls *.bed | cut -d"." -f1`
  do
    # submitting tensorQTL jobs for each tissue type
    echo $dataset $tissue
    sbatch --export=ARGS1=${dataset},ARGS2=${tissue} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/tensorQTL_mQTL_ALL.sh
  done
done
```

# Generating a combined plot of inferred cell type proportions across tissue types
```{r}
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/PLOT_CELLTYPE_FRACTIONS.R
```

# Generating Q-Q plots for imQTLs
```{bash}
for dataset in GTEx HEALS
do
  cd /gpfs/data/pierce-lab/james.li/imQTL/output/${dataset}/imQTL/top_assoc
  tissue_cell_combination_list=`ls tensorQTL_imQTL_*.cis_qtl_top_assoc.txt.gz | cut -d"." -f1 | uniq`
  for combination in ${tissue_cell_combination_list}
  do
    echo ${dataset} ${combination}
    sbatch --export=ARGS1=${dataset},ARGS2=${combination} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/PLOT_QQPLOT.sh
  done
done
```

# Extracting counts of mQTLs and imQTLs
```{bash}
# identifying number of mapped imQTLs
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/PLOT_NUM_imQTL.R
# identifying number of mapped mQTLs
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/PLOT_NUM_mQTL.R
# identifying CpGs mapped to imQTLs but not mQTLs
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/IDENTIFY_CPG_IMQTLS_NOT_MQTLS.R
```

# Evaluating distances between CpGs and variants between imQTLs and mQTLs
```{bash}
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/DISTANCE_CPG_VARIANT.R
```

# Examining directional consistency of marginal and interaction term effects for these imQTLs and generating regional plots
```{bash}
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/PROCESS_QTL_EFFECTS_REGIONAL_PLOT.R

Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/PLOT_INTERACTION_MQTL_BOXPLOT.R
```

# Performing validation of whole blood results
```{bash}
# obtaining interaction term estimates for the whole blood imQTLs in HEALS and GTEx
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/VALIDATION_WB_IMQTL_PROCESS_EFFECTS.R

# parsing through these validation results and generating plots
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/VALIDATION_WB_IMQTL_PARSE_EFFECTS.R
```

# Assessing whether whole blood imQTLs mapped in HEALS tend to reside in differentially methylated regions by inferred cell type proportions in GTEx whole blood samples
```{bash}
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/WB_DIFFERENTIALLY_METHYLATED_REGIONS.R
```

# Comparing interaction terms of imQTLs with consistent interaction and marginal effects across tissues
```{bash}
# identify IDs for all significant cpg/variant pairs
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/EXTRACT_CPG_VARIANT_PAIRID_SIG_imQTL.R

# obtaining mashr inputs for all selected sig and random cpg/variant pairs
for dataset in GTEx HEALS
do
  cd /gpfs/data/pierce-lab/james.li/imQTL/output/${dataset}/imQTL/top_assoc
  tissue_cell_combination_list=`ls tensorQTL_imQTL_*.cis_qtl_top_assoc.txt.gz | cut -d"." -f1 | uniq | grep -v "Eosino"`
  for combination in ${tissue_cell_combination_list}
  do
    echo ${dataset} ${combination}
    sbatch --export=ARGS1=${dataset},ARGS2=${combination} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/PARQUET_EXTRACT_VARIANTS.sh
  done
done

# comparing interaction terms of imQTLs across tissues and cell types
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/RUN_CROSS_TISSUE_COMPARE_wb.R
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/RUN_CROSS_TISSUE_COMPARE_colon.R
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/RUN_CROSS_TISSUE_COMPARE_lung.R

# examining whether interaction terms flip for major cell types
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/MAJOR_CELLTYPE_wb_Neutro.R
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/MAJOR_CELLTYPE_colon_Lym.R
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/MAJOR_CELLTYPE_lung_Endo.R
```

# Examine pleiotropy of lead variants
```{bash}
# extracting pleiotropic variants and metrics from parquet files
python /gpfs/data/pierce-lab/james.li/imQTL/code/python/PLEIOTROPY_ANALYSIS.py

# creating plots to characterize pleiotropy
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/PLOT_PLEIOTROPY_ANALYSIS.R
```

# Identifying number of conditionally independent signals at each imQTL locus
```{bash}
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/COUNTING_CONDITIONALLY_INDEPENDENT_IMQTLS.R
```

# Identifying candidate cell type-specific mQTLs
```{bash}
# filtering by interaction term 
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/CANDIDATE_CT_SPECIFIC_IMQTL.R
# filtering by top 50% of cell types
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/CANDIDATE_CT_SPECIFIC_IMQTL_2.R
# plotting these cell type specific imQTLs
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/CANDIDATE_CT_SPECIFIC_IMQTL_REGRESSION_BOXPLOTS.R
# plotting an imQTL with opposite directionality between two imQTLs
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/CANDIDATE_CT_SPECIFIC_IMQTL_EXAMPLE_INDEL.R
```

# Mapping eQTLs that have been previously discovered in GTEx
```{bash}
# set working directory
cd /gpfs/data/pierce-lab/james.li/imQTL/data/ADDITIONAL/GTEx_eQTL_v8/input

# Loop through all files in the current directory
for file in *; do
  # Perform substitutions
  new_file=$(echo "$file" \
    | sed 's/Colon_Transverse/colon/' \
    | sed 's/Whole_Blood/wb/' \
    | sed 's/Lung/lung/' \
    | sed 's/Ovary/ovary/' \
    | sed 's/Prostate/prostate/')

  # Rename the file if the name has changed
  if [[ "$file" != "$new_file" ]]; then
    mv "$file" "$new_file"
    echo "Renamed: $file -> $new_file"
  fi
done

# running tensorQTL
for tissue in colon lung ovary prostate wb
do
  sbatch --export=ARGS1=${tissue} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/tensorQTL_eQTL_ALL.sh
done
```

# Performing coloc of imQTLs with GWAS summary statistics
```{bash}
# processing cancer GWAS summary statistics
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/PROCESS_CANCER_GWAS.R

# preparing lists for extraction of variants nearby imqtls that are tested for their association with a given cpg 
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/GWAS_COLOC_PREPARE_EXTRACT_IMQTL.R

# extracting variants within +/- 250 kb of a given lead variant for a particular cpg mapped to an imqtl
for extract_list in /gpfs/data/pierce-lab/james.li/imQTL/output/GWAS_coloc/extract_imqtl_list/*
do
  sbatch --export=ARGS1=${extract_list} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/GWAS_COLOC_EXTRACT_IMQTL_DATA.sh
done

# performing coloc on each gwas summary statistics file
for gwas_file in /gpfs/data/pierce-lab/james.li/GWAS_Trait_87/*.txt.gz
do
  sbatch --export=ARGS1=${gwas_file} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/GWAS_COLOC_RUN.sh
done

# plotting results and identifying imQTLs with multiple coloc hits [utilize this rscript after all of the eQTL/marginal effect QTL analysis below] 
## so the GWAS_COLOC_PLOT script also generates an arc chart of coloc with both eQTL and GWAS
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/GWAS_COLOC_PLOT.R
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/GWAS_COLOC_PLOT_custom_prior.R
```

# Performing coloc of mQTL signals at mQTLs with GWAS
```{bash}
# convert mQTL parquet files to tsv
python /gpfs/data/pierce-lab/james.li/imQTL/code/python/CONVERT_GTEX_MQTL_PARQUET_TSV.py

# extract mQTL associations around each imQTL within +/- 250 kb for a given CpG
for extract_list in /gpfs/data/pierce-lab/james.li/imQTL/output/GWAS_coloc/extract_imqtl_list/*
do
  sbatch --export=ARGS1=${extract_list} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/GWAS_COLOC_EXTRACT_MQTL_DATA.sh
done

# performing GWAS-mQTL coloc by iterating through each GWAS summary statistics file
for gwas_file in /gpfs/data/pierce-lab/james.li/GWAS_Trait_87/*.txt.gz
do
  sbatch --export=ARGS1=${gwas_file} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/GWAS_MQTL_COLOC_RUN.sh
done

# analyzing mQTL and imQTL coloc with GWAS
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/GWAS_COLOC_PARSE_MQTL.R
```

# Performing coloc of imQTLs with eQTLs
```{bash}
# convert GTEx eQTLs from parquet to tsv format
python /gpfs/data/pierce-lab/james.li/imQTL/code/python/CONVERT_GTEX_EQTL_PARQUET_TSV.py

# performing coloc of imQTLs with eQTLs (using extracted imQTL lists from the GWAS coloc)
for extract_list in /gpfs/data/pierce-lab/james.li/imQTL/output/GWAS_coloc/extract_imqtl_list/*
do
  sbatch --export=ARGS1=${extract_list} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/EQTL_COLOC_RUN.sh
done

# examining eqtl coloc results and plotting
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/EQTL_COLOC_EXAMINE.R
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/EQTL_COLOC_EXAMINE_custom_prior.R
```

# Performing enrichment analyses for genomic context
```{bash}
# assembling all chromatin segmentation states files in hg38
bash /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/ASSEMBLING_CHROMATIN_SEGMENTATION_STATE_BED_hg38.sh

# moving all target hg38 bed/interval genomic annotation files to the same directory
input_dir_UCSC=/gpfs/data/pierce-lab/james.li/imQTL/data/ADDITIONAL/UCSC_TABLE_BROWSER_hg38
input_dir_ENCODE5=/gpfs/data/pierce-lab/james.li/imQTL/data/ADDITIONAL/ENCODE5_hg38
input_dir_CHROMATIN=/gpfs/data/pierce-lab/james.li/imQTL/data/ADDITIONAL/CHROMATIN_SEGMENTATION/hg38/mapped
output_dir=/gpfs/data/pierce-lab/james.li/imQTL/data/ADDITIONAL/TARGET_GENOMIC_ANNOTATION_BED_hg38
for tmp_dir in ${input_dir_UCSC} ${input_dir_ENCODE5} ${input_dir_CHROMATIN}
do
  cd ${tmp_dir}
  cp * ${output_dir}/
done
cd /gpfs/data/pierce-lab/james.li/imQTL/data/ADDITIONAL/TARGET_GENOMIC_ANNOTATION_BED_hg38
cat cpgShelf1.bed cpgShelf2.bed cpgIsland.bed > cpgShelf.bed
cat cpgShore1.bed cpgShore2.bed cpgIsland.bed > cpgShore.bed
rm cpgShelf1.bed cpgShelf2.bed cpgShore1.bed cpgShore2.bed

# obtaining background/tested variant and cpg bed files for enrichment analysis (later, imQTL and mQTL variants and cpgs will be extracted from these total background/tested lists)
bash /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/ENRICHMENT_ANALYSIS_ASSEMBLE_BACKGROUND_INPUTS.sh

# obtaining enrichment annotations for each file
bed_file_dir=/gpfs/data/pierce-lab/james.li/imQTL/data/ADDITIONAL/ENRICHMENT_ANALYSIS/BACKGROUND/bed
interval_file_dir=/gpfs/data/pierce-lab/james.li/imQTL/data/ADDITIONAL/TARGET_GENOMIC_ANNOTATION_BED_hg38
output_bed_dir=/gpfs/data/pierce-lab/james.li/imQTL/output/ENRICHMENT_ANALYSIS/bedtools_output
# loading modules
module load gcc
module load bedtools
# running the for-loop, takes around 10-15 minutes
for bed_file in `ls ${bed_file_dir}* | head`
do
  for interval_file in `ls ${interval_file_dir}*`
  do
    echo ${bed_file} ${interval_file}
    bedtools intersect -a ${bed_file_dir}/${bed_file} -b ${interval_file_dir}/${interval_file} -wa -wb > "${output_bed_dir}/${bed_file}-${interval_file}"
  done
done

# processing and plotting enrichment results
## general parsing
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/ENRICHMENT_ANALYSIS_PARSING.R
## plotting genomic context
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/ENRICHMENT_ANALYSIS_PLOT_GENOMIC_CONTEXT.R
## plotting chromatin states
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/ENRICHMENT_ANALYSIS_PLOT_CHROMATIN.R
## plotting TFBS
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/ENRICHMENT_ANALYSIS_TFBS.R
```


# Making additional figures and tables for paper
```{bash}
# creating miscellaneous plots for figures in the manuscript 
## code to create interaction box plots for select examples, need to run the code example by example
## includes supplementary figures associated with Figure 5 as well
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/FIGURE2_PANEL_GENERATION.R
## code for regional plot creation of examples, each code is a different region
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/TARGET_REGIONAL_EQTL_CUSTOM_1.R
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/TARGET_REGIONAL_EQTL_CUSTOM_2.R
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/TARGET_REGIONAL_MQTL_CUSTOM_1.R
# Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/TARGET_REGIONAL_MQTL_CUSTOM_2.R
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/TARGET_REGIONAL_MQTL_CUSTOM_3.R

# assembling a GWAS meta-data table for the supplementary material
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/ASSEMBLING_GWAS_METADATA_TABLE.R

# parsing summary statistics for all imQTLs and also CT-specific imQTLs
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/PARSING_SUMSTATS_IMQTL_AND_CTSPECIFIC.R

# obtaining summarys of each covariate and also DNAm PC associations with covariates
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/PLOTTING_COVARIATE_CORRPLOTS.R

# sensitivity analyses for covariate adjustment
## removing DNAm PCs that were correlated with genetic PCs or estimated cell type proportions
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/SENSITIVITY_ANALYSIS_COVADJUST_REMOVEcol_NORMct.R
## modeling raw cell type proportions rather than INT-transformed cell type proportions while still utilizing all DNAm PCs 
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/SENSITIVITY_ANALYSIS_COVADJUST_ORIGINALcol_RAWct.R
## summarizing and outputting metrics for these sensitivity analyses on covariate adjustment
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/SENSITIVITY_ANALYSES_COVADJUST_SUMMARIZE.R

# sensitivity analysis for cell type deconvolution panel in both GTEx and HEALS
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/SENSITIVITY_ANALYSIS_DECONVOLUTION_EPIDISH_REFERENCE_COMPARISON_HEALS.R
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/SENSITIVITY_ANALYSIS_DECONVOLUTION_EPIDISH_REFERENCE_COMPARISON_GTEX.R
```


#################
# Revision Code #
#################

# Modifying box plots
```{bash}
# the actual code
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/REVISION_FIGURE2_BOXPLOTS.R
# the generic code
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/REVISION_FIGURE2_PANEL_GENERATION.R
```

# Validation of MESA imQTLs in HEALS
```{bash}
# MESA FDR<0.05 in HEALS
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/MESA_VALIDATION_FULL_HEALS_SUMSTATS.R
# MESA lead variants in HEALS
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/MESA_VALIDATION_LEAD_VARIANTS.R
```

# Performing coloc with cell-type-specific eQTLs
```{bash}
########################
# default coloc priors #
########################
# performing coloc with sc-eQTLs detected in each cell type 
## PBMCs
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/SCEQTL_COLOC_RUN_PBMC.R
## neutrophils
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/SCEQTL_COLOC_RUN_NEUTROPHIL.R
## plotting pie charts
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/SCEQTL_COLOC_EXAMINE.R

#######################
# custom coloc priors #
#######################
# performing coloc with sc-eQTLs detected in each cell type 
## PBMCs
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/SCEQTL_COLOC_RUN_PBMC_custom_prior.R
## neutrophils
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/SCEQTL_COLOC_RUN_NEUTROPHIL_custom_prior.R
## plotting pie charts
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/SCEQTL_COLOC_EXAMINE_custom_prior.R

# filtering coloc results to only those in "cell-type-specific" eQTLs
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/SCEQTL_CTSPECIFIC.R
```


# GWAS coloc revisions
```{bash}
# re-creating GWAS dictionary
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/GWAS_87_DICTIONARY_CREATION.R

# re-creating Figures 5B&C
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/REVISION_GWAS_COLOC_PLOT.R

##############################
# running coloc on all mQTLs #
##############################
# extracting mqtl windows for coloc
for mqtl_chunk in "${mqtl_chunk_list[@]}"
do
  sbatch --export=ARGS1=${mqtl_chunk} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/GWAS_COLOC_BULKMQTL_EXTRACT_WINDOWS.sh
done

# performing GWAS-mQTL coloc by iterating through each GWAS summary statistics file
for gwas_file in /gpfs/data/pierce-lab/james.li/GWAS_Trait_87/*.txt.gz
do
  sbatch --export=ARGS1=${gwas_file} /gpfs/data/pierce-lab/james.li/imQTL/code/sbatch/GWAS_COLOC_BULKMQTL_RUN.sh
done

# plotting and evaluating coloc results for bulk mQTLs
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/GWAS_COLOC_BULKMQTL_PLOT.R

# comparing imQTL vs bulk mQTL coloc with GWAS
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/SUMMARIZE_COMPARE_IMQTL_MQTL_GWAS.R
```

# Consolidation of cell-type specificity
```{bash}
Rscript /gpfs/data/pierce-lab/james.li/imQTL/code/rscripts/REVISION_CONSOLIDATE_CELLTYPESPEC_VS_OTHER_IMQTLS.R
```
